Search enrichment by protein

### 2025-02-21 IndividualStudies/AT_2025.qmd
Adding Gene Ontology search

>>>>

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
```
:::

#### Molecular Function

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))

#### Biological Process

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))

### 2025-02-21 IndividualStudies/DH_2017.qmd
Adding Gene Ontology search

## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(stringr)
library(pheatmap)
library(here)
library(heatmaply)
library(ggvenn)
library(scales)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
  mutate(gene_name = str_extract(Description, "GN=([^\\s]+)") |> str_remove("GN=")) |>
  mutate(Species = str_extract(Description, "OS=([^=]+?)\\sGN=") |> str_remove("OS=") |> str_remove("GN=")) |>
  filter(Species == "Homo sapiens ") |>
  mutate(PSM_Sph = (PSM_Sph1 + PSM_Sph2) / 2,
         PSM_FA = (PSM_FA1 + PSM_FA2) / 2,
         PSM_DAG = (PSM_DAG1 + PSM_DAG2) /2) |>
  select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
  arrange(gene_name) |>
  group_by(gene_name) |>
  summarise(PSM_DAG = mean(PSM_DAG),
            PSM_FA = mean(PSM_FA),
            PSM_Sph = mean(PSM_Sph))
```

@@

#### Heat map
:::{.border}
```{r, echo=FALSE, fig.height=10, warning=FALSE}

DH_2017_data_long <- DH_2017_data |>
  pivot_longer(cols = starts_with("PSM_"),
              names_to = "variable",
              names_prefix = "PSM_",
              values_to = "value") |>
  mutate(name = gene_name) |>
  select(name, variable, value)
  # mutate(OriginalValues = value) |>
  # mutate(value = case_when(value < 20 ~ value,
  #                           value >= 20 ~ 20))

@@

Sph_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_Sph > 0) |>
  select(PSM_Sph)

FA_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_FA > 0) |>
  select(PSM_FA)

DAG_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_DAG > 0) |>
  select(PSM_DAG)

>>>>

## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(stringr)
library(here)
library(heatmaply)
library(ggvenn)
library(scales)
## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
  mutate(gene_name = str_extract(Description, "GN=([^\\s]+)") |> str_remove("GN=")) |>
  mutate(Species = str_extract(Description, "OS=([^=]+?)\\sGN=") |> str_remove("OS=") |> str_remove("GN=")) |>
  filter(Species == "Homo sapiens ") |>
  mutate(PSM_Sph = (PSM_Sph1 + PSM_Sph2) / 2,
         PSM_FA = (PSM_FA1 + PSM_FA2) / 2,
         PSM_DAG = (PSM_DAG1 + PSM_DAG2) /2) |>
  dplyr::select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
  arrange(gene_name) |>
  group_by(gene_name) |>
  summarise(PSM_DAG = mean(PSM_DAG),
            PSM_FA = mean(PSM_FA),
            PSM_Sph = mean(PSM_Sph))
```

@@

#### Heat map

Depicted below are the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA.
:::{.border}
```{r, echo=FALSE, fig.height=10, warning=FALSE}

DH_2017_data_long <- DH_2017_data |>
  pivot_longer(cols = starts_with("PSM_"),
              names_to = "variable",
              names_prefix = "PSM_",
              values_to = "value") |>
  mutate(name = gene_name) |>
  dplyr::select(name, variable, value)
  # mutate(OriginalValues = value) |>
  # mutate(value = case_when(value < 20 ~ value,
  #                           value >= 20 ~ 20))

@@

Sph_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_Sph > 0) |>
  dplyr::select(PSM_Sph)

FA_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_FA > 0) |>
  dplyr::select(PSM_FA)

DAG_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_DAG > 0) |>
  dplyr::select(PSM_DAG)

### 2025-02-21 IndividualStudies/SF_2024.qmd
Adding Gene Ontology search

@@

## Enriched Proteins

@@

SF_2024_data <- SF_2024_data |>
  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

>>>>

:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

#### Molecular Function

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

#### Biological Process

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

@@

## Data exploration and download

@@

SF_2024_data <- SF_2024_data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

### 2025-02-21 IndividualStudies/SF_2024_B.qmd
Adding Gene Ontology search

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")

@@

## Enriched Proteins

>>>>

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies//DataTables/SF_Chem_Comm_2024_download.csv"))

@@

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

#### Molecular Function

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

#### Biological Process

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

:::

## Data exploration and download

### 2025-02-21 LipidProbe/1-10_FattyAcid.qmd
Adding Gene Ontology search

@@

##### Data

>>>>

```
:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

::: {.panel-tabset}

#### Cell Compartment

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

#### Molecular Function

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

#### Biological Process

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

```
:::
:::

## Data exploration and download

### 2025-02-21 LipidProbe/8-3_FattyAcid.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

---
title: "Trifunctional 8-3 Fatty Acid"
html: default
---

@@

##### Data

@@

# Here is the code to make the filterable lists shown in the crosstalk table below

SF_2024_data <- SF_2024_data |>
  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

>>>>

---
title: "Trifunctional 8-3 Fatty Acid"
crossref: 
  ref-hyperlink: true # (default is true)
prefer-html: true
html: default
---

@@

#### Biological Process

@@

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

```
:::
:::

## Data exploration and download

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# Here is the code to make the filterable lists shown in the crosstalk table below

SF_2024_data <- SF_2024_data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

### 2025-02-21 LipidProbe/PhosphatidicAcid.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

---
title: "Trifunctional Phosphatidic Acid"
---

@@

##### Data

@@

AT_2025_Long <- AT_2025_Long |>
  select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation)

>>>>

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
---

@@

:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
```
:::

#### Molecular Function

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))

#### Biological Process

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))

```
:::
:::

## Data exploration and download

@@

AT_2025_Long <- AT_2025_Long |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation)

### 2025-02-21 LipidProbe/Phosphatidylethanolamine.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

---
title: "Trifunctional Phosphatidylethanolamine"
---

@@

##### Data

>>>>

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
---

@@

```
:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
```
:::

#### Molecular Function

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))

#### Biological Process

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))

```
:::
:::

## Data exploration and download

### 2025-02-21 LipidProbe/Sphinganine.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

---
title: "Trifunctional sphinganine"
---

@@

@@

SF_2024_data <- SF_2024_data |>
  select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation)

>>>>

---
title: "Trifunctional sphinganine"
prefer-html: true
---

@@

```
:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

#### Molecular Function

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

SF_2024_data <- SF_2024_data |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation)

### 2025-02-21 SearchByProtein/SearchByProtein.qmd
Adding Gene Ontology search

datawhole <- data |>
	select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
	mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
					Study = case_when(LipidProbe == "1-10 FA" ~ "Farley et al. 2024 B; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "8-3 FA" ~ "Farley et al. 2024 B; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "Sph" ~ "Farley et al. 2024 A; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "Spa" ~ "Farley et al. 2024 A; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "PE" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														LipidProbe == "PA" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														LipidProbe == "PA" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe) |>
	glimpse()

>>>>

datawhole <- data |>
	dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
	mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
					Study = case_when(LipidProbe == "1-10 FA" ~ "Farley et al. 2024 B; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "8-3 FA" ~ "Farley et al. 2024 B; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "Sph" ~ "Farley et al. 2024 A; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "Spa" ~ "Farley et al. 2024 A; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "PE" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														LipidProbe == "PA" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														LipidProbe == "PA" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe) |>
	glimpse()
